\textbf{ Matching the forecast horizon with the relevant ecological processes }

### 2019-10-15 doc/manuscript.tex
small figure edits

\begin{figure}[tbp]
\centering
\includegraphics[width=0.4 \textwidth]{spatial&temporal_model.png}
\caption{(A) Reaction norms of the three genotypes. (B) The spatial pattern of individual genotypes (colors) and total population abundance (black) at sites arrayed across a gradient of mean annual temperature. The dashed line shows predictions from an empirical ``spatial model," a linear regression that describes mean population size as a function of mean temperature. (C) The relationship between annual temperature and per capita growth rate at a location with a mean temperature that favors the cold-adapted genotype. Colors show population size (the blue to red gradient depicting high to low population density), which influences the population growth rate through density dependence. }
\label{fig:evo_evo_spatial_temporal_models}
\end{figure}

>>>>

\begin{figure}[tbp]
\centering
\includegraphics[width=0.4 \textwidth]{spatial&temporal_model.png}
\caption{(A) Reaction norms of the three genotypes. (B) The spatial pattern of individual genotypes (colors) and total population abundance (black) at sites arrayed across a gradient of mean annual temperature. The dashed line shows predictions from an empirical ``spatial model," a linear regression that describes mean population size as a function of mean temperature. (C) The relationship between annual temperature and per capita growth rate at a location with a mean temperature that favors the cold-adapted genotype. Colors show population size (the green to brown gradient depicting low to high population density), which influences the population growth rate through density dependence. }
\label{fig:evo_evo_spatial_temporal_models}
\end{figure}
